An Exegesis of Ontological Hermeneutics

### 2022-10-29 responseToReviews/response_to_reviewers.tex

   The models in Section II do not include a carrier frequency component,
    since they are expressed in a complex baseband representation.  But they
    do include a Doppler frequency component: $\theta_A$ and $\theta_I$ are
    time varying, as noted in the original text:
    \begin{quotation}
      $P_{\rm A}$, $\tau_{\rm A}$, and $\theta_{\rm A}$ are assumed to vary
      with time, but their time dependency is suppressed for notational
      simplicity.
    \end{quotation}
    Also, the relative time variation between $\theta_{\rm A}$ and
    $\hat{\theta}$ -- the variation that could cause tracking stress -- is
    explicitly noted later on by the notation $\theta_{{\rm A}k}$.

{\textit{p6: Technically, R(tau) is a cross correlation function.}}

  {{Agreed.  But the technical distiction was already noted in the
        original manuscript:}}
    \begin{quotation}
      The function $R(\tau) = E[C_r(t)C_{\ell}(t - \tau)]$, often called the
      autocorrelation function of $C_r(t)$ even though, strictly speaking,
      $C_{\ell}(t)$ may be slightly different from $C_r(t)$, approximates the
      interaction between $C_r(t)$ and $C_{\ell}(t)$ over the correlation and
      accumulation operations.
    \end{quotation}

{\textit{section VIII: How is the performance compared against
      other published methods?}}

   Of the various signal authentication techniques mentioned in the
    paper's introduction (which offers an up-to-date summary of techniques),
    this paper's approach can be fairly compared only with a small set of
    practical near-term GNSS signal authentication techniques that do not
    require changes to GNSS signals-in-space, are receiver-autonomous,
    low-cost, require no additional hardware, and can be implemented via a
    software or firmware update. Existing techniques in this category include
    monitoring the total received power via the Automatic Gain Control (AGC)
    setpoint~\cite{akos2012s}, and monitoring autocorrelation profile
    distortion~\cite{ledvina2010cgr, cavaleri2010dscc, huang2016gnss}.  These
    tecniques can be viewed as special cases of the current paper's technique.
    The ``blindspot'' from which these techniques suffer due to their ignoring
    one or the other of received power or correlation function distortion can
    be appreciated emph{a priori}: A received power monitor that ignores
    correlation distortion may not detect a low-power spoofer. Moreover,
    because a power-monitoring-only technique does not distinguish between
    spoofing and jamming, its alarm rate can become intolerable in urban areas
    where so-called personal privacy devices (PPDs, small GNSS
    jammers)~\cite{mitch2012kyejam} are common.  For their part, the
    distortion-monitoring approaches in \cite{ledvina2010cgr,
      cavaleri2010dscc, huang2016gnss} ignore total received power, and thus
    can be fooled by a spoofer transmitting with a significant power advantage
    over the authentic signals, which, by action of the AGC, forces the
    authentic signals under the noise floor, leaving a distortion-free
    correlation function~\cite{humphreys2011ds}.

    This \emph{a priori} comparison is included in the paper's original
    manuscript.  It is also clear from the optimal decision regions shown in
    Fig. 7 that ignoring one or the other of $P_k$ or $D_k$ (as the prior work
    in this area does), would be sub-optimal.  Therefore, we believe that the
    paper convincingly establishes that its approach is superior to other
    approaches in the relevant category for comparison.

{\textit{More details on the test data are expected.}}

  {{Thank you. An additional reference for the TEXBAT data set was
        included.  Between the three references to the TEXBAT data, and the
        two references on the ``RNL Multipath and Interference Recordings,''
        we believe the test data are now adequately detailed.}}

{\textit{I am not sure that the paper includes enough results to
      show how well the proposed method functions with weak signals. For
      example, if the target signal is weak, interference from other
      GNSS signals may also confuse the detector, since it can be
      observed as multipath or interference. It may trigger more false
      alarms.}}

  {{The reviewer raises a good point here: it is possible that near-far
        effects (interaction of weak signals with very strong signals due to
        imperfect orthogonality of their spreading codes) could cause
        distortion that would lead to false spoofing alarms.  The reviewer
        encourages testing to determine if the proposed method works in
        near-far cases with a large gap between the power of the strongest and
        weakest signal.  In fact, the clean data set {\tt cd0}, {\tt wd0}, and
        {\tt wd1} do include a fairly wide range of signal powers.  The most
        powerful signals show $C/N_0 \approx 52$ dB-Hz, while the weakest
        signals are at 35 dB-Hz.  This constitutes 17-dB difference in signal
        power, yet no false spoofing alarms were raised (cf. Table III).  An
        even wider dynamic range could be tested, but the reviewer is
        requested to keep in mind that the difficulty of distinguishing
        multipath from low-power spoofing when severe shadowing is present was
        already treated in Section III:

        \begin{quotation}
          On the other hand, the severe shadowing experienced by mobile
          receivers can cause $\eta > 1$, especially in urban environments
          where surrounding buildings simultaneously attenuate and reflect
          authentic signals \cite{steingass2004measuring}.  In these
          situations, there is no practical upper limit on $\eta$ because the
          direct-path authentic signal may be attenuated by 50 dB or more. It
          is not possible to reliably distinguish multipath from low-power
          spoofing in such circumstances.

          One can avoid this difficulty by applying this paper's detection
          test only when the authentic signal $r_{\rm A}(t)$ is received
          without severe shadowing, in which case the probability that
          $\eta > 1$ under $H_1$ again becomes negligible. In particular, the
          multipath model developed below assumes that $r_{\rm A}(t)$ is
          attenuated less than 6 dB by shadowing.  In practice, one simply
          excludes cases in which the received power $P_k$ is not unusually
          high yet the measured carrier-to-noise ratio $C/N_0$ drops by more
          than 6 dB from its modeled value for an unobstructed authentic
          signal.
        \end{quotation}

        In other words, our approach avoids the effects of severe shadowing by
        applying the PD detector only to signals that have been attenuated
        less than 6 dB by shadowing.  With this exclusion, and with the
        false-alarm-free performance of the paper's methods on the three $H_0$
        data sets, in additions to thorough simulation testing in Section VI,
        we believe that the spoofing false alarm rate under $H_0$ will be
        negligible.}}

{\textit{For the power metric introduced in IV.A, it is not
      entirely clear how it can be implemented. How precise does
      the power measurement has to be in order for this method
      to be applicable? In practice, we use carrier to noise
      ratio to gauge signal strength. Depending on the
      implementation choice, it may not be very precise for weak
      signals, or signals with interference. }}

   Details on how to measure $P_k$ in practice are included in this
    paragraph from Section IV.A:

    \begin{quotation}
      Receivers with sufficient dynamic range in the discrete samples produced
      from $r_{\rm C}(t)$ do not require an AGC and so can compute received
      power directly by averaging the squared modulus of these samples.  Let
      $W_{P}$ be the bandwidth over which $P_k$ is to be measured.  If $W_P$
      is narrower than the receiver front-end's native bandwidth, then
      $r_{\rm C}(t)$ must be filtered to isolate the desired spectral
      interval.  Fig. 3 shows 2- and 8-MHz bands for $P_k$,
      with Fig. 4 showing the corresponding power time
      histories.  In a receiver whose front end is equipped with an AGC, $P_k$
      is measured indirectly through the AGC setpoint \cite{akos2012s}.  In
      this case $W_{P}$ is equivalent to the front-end noise-equivalent
      bandwith.
    \end{quotation}

    Details on measuring the power indirectly through the AGC setpoint are
    found in \cite{akos2012s}, referenced within this paragraph.

      Note that measuring aggregate received power is different from measuring
      $C/N_0$.  Consider that, if effective $N_0$ rises in a spoofing attack
      commensurate with carrier power $C$, then $C/N_0$ will remain constant
      even as $P_k$ rises.

      How accurately does $P_k$ need to be measured to be useful?  We have
      modified the manuscript in two places to indicate that the paper's
      detection test assumes $\sigma_P = 0.4$ dB.  This is roughly four times
      the standard deviation due to natural variation in a high quality
      receiver in a quiet RF environment (see the top panel in Fig. 4 and the
      discussion within the text).  Receivers whose measurement of $P_k$ is
      significantly less precise than this, due to quantization or inaccuracy
      in the AGC set point-to-$P_k$ mapping, will see their ability to detect
      low-power spoofing and jamming reduced.

      Note that \cite{akos2012s} showed that the precision of the AGC
      measurement as a proxy for in-band power is much better than the natural
      variation in the AGC (see Fig. 7 in \cite{akos2012s}).  This indicates
      that $P_k$ can be reliably obtained from the AGC measurement (to within
      a constant offset that can be calibrated in a quiet RF environment).

{\textit{Eq 10 assumes that the code phase can be observed
      by maximizing correlation function. Ideally this
      assumption would be nice to have. However, with weak
      signals or limited bandwidth, it is usually not practical
      to do that. The early-late code discriminator is likely to
      be more sensitive than the peak point in some
      scenarios. What is the sensitivity level of the detector
      against errors made in this step? }}

   This paper's assumed recipe for determination of $\hat{\tau}$ is given
    by \[ \hat{\tau} = \arg \max_\tau \xi_k(\tau)  \]  But this recipe is
    only used for modeling purposes.  As the reviewer notes, in practice the
    recipe will be some type of early-late code discriminator, possibly with
    multiple early and late taps.

    The actual receiver used to generate the observables that were processed
    by the PD detector to yield the results in Section VII, the GRID
    science-grade software-defined receiver \cite{lightsey2013demonstration},
    does in fact use an early-minus-late discriminator to obtain $\hat{\tau}$.
    The fact that the PD detector worked well when using the GRID-produced
    observables---even in the case of signals as weak as $35$
    dB-Hz---indicates that the method is not highly sensitive to how
    $\hat{\tau}$ is obtained.

\bibliographystyle{IEEEtran} 
\bibliography{pangea}
\end{document}
